%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
% Medium Length Professional CV
% LaTeX Template
% Version 3.0 (December 17, 2022)
%
% This template originates from:
% https://www.LaTeXTemplates.com
%
% Author:
% Vel (vel@latextemplates.com)
%
% Original author:
% Trey Hunner (http://www.treyhunner.com/)
%
% License:
% CC BY-NC-SA 4.0 (https://creativecommons.org/licenses/by-nc-sa/4.0/)
%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

%----------------------------------------------------------------------------------------
%	PACKAGES AND OTHER DOCUMENT CONFIGURATIONS
%----------------------------------------------------------------------------------------

\documentclass[
	%a4paper, % Uncomment for A4 paper size (default is US letter)
	11pt, % Default font size, can use 10pt, 11pt or 12pt
]{resume} % Use the resume class

\usepackage{ebgaramond} % Use the EB Garamond font
\usepackage{hyperref}

%------------------------------------------------

\name{Eleanor Rachel Sinden} % Your name to appear at the top

% You can use the \address command up to 3 times for 3 different addresses or pieces of contact information
% Any new lines (\\) you use in the \address commands will be converted to symbols, so each address will appear as a single line.

\address{Phone: 07494364085 \\ Email: \href{mailto:ellymurrell1@gmail.com}{ellymurrell1@gmail.com} \\ GitHub: \href{https://github.com/ellypeop}{github.com/ellypeop}} % Contact information


\address{Folkestone, Kent} % Main address

%----------------------------------------------------------------------------------------

\begin{document}

%----------------------------------------------------------------------------------------
%	PROFESSIONAL SUMMARY SECTION
%----------------------------------------------------------------------------------------

\begin{rSection}{Professional Summary}

\textbf{MSc Computer Science graduate seeking an entry-level software engineering position.} Proficient with Python, Java, SQL, and UML. I am interested in quantum computing and software engineering; my dissertation compared two quantum UML adaptations by modelling Qiskit code through sequence and class diagrams. I was awarded a paid internship during my studies, where I developed Power BI dashboards to support DRTV fundraising campaigns for charities. I am detail-oriented, adaptable, and capable of learning new technologies quickly, with a proven ability for collaboration, problem-solving and delivering effective software solutions.

\end{rSection}

%----------------------------------------------------------------------------------------

%	TECHNICAL STRENGTHS SECTION
%----------------------------------------------------------------------------------------

\begin{rSection}{Technical Strengths}

    \begin{tabular}{@{} p{4cm} p{11cm} @{}}
        \textbf{Languages} & Python, Java, SQL, UML, DAX \\ 
        \textbf{Software and Tools} & GitHub, Power BI, IntelliJ, PyCharm, SSMS, Microsoft Copilot Studio \\ 
        \textbf{Technologies and Frameworks} & TensorFlow, PyTorch, Qiskit, Scikit-learn, NumPy, Stable Diffusion, Gymnasium\\
    \end{tabular}

\end{rSection}



%----------------------------------------------------------------------------------------
%	WORK EXPERIENCE SECTION
%----------------------------------------------------------------------------------------

\begin{rSection}{Employment}

	\begin{rSubsection}{Giftease Solutions}{June 2024 - September 2024}{AI Engineer Intern}{Remote}
		\item Designed and implemented DRTV fundraising dashboards using SQL and Power BI, automating campaign performance insights. Presented dashboards in a client meeting with plans for further development into a final product.
		\item Integrated external datasets via web scraping and created custom map visuals using JSON files.
        \item Built a Microsoft Copilot tailored for Gift Aid advisory services that automates customised communications based on industry guidelines. 
        \item Independently learned Microsoft Copilot Studio and created dashboards, demonstrating self-motivation and the ability to deliver solutions with minimal supervision.
        \item Applied data normalisation techniques to calculate weighted donations, improving targeted marketing strategies.
	\end{rSubsection}

%------------------------------------------------

	\begin{rSubsection}{Spain Brothers \& Co}{September 2022 - August 2023}{Tax Technician}{Canterbury, Kent}
		\item Computed and submitted individual tax returns for clients with diverse income sources, ensuring accuracy and compliance with regulations.
		\item Led client meetings and conducted research to resolve complex taxation issues, applying problem-solving and analytical skills.
		\item Collaborated with accounts and corporation tax departments to develop effective tax planning strategies.
		\item Monitored legislative changes and adapted workflows to align with updated regulations.
	\end{rSubsection}

%------------------------------------------------

	\begin{rSubsection}{RIFT Refunds}{November 2020 - September 2022}{Personal Tax Specialist}{Ashford,Kent}
		\item Managed a caseload of over 140 clients, efficiently preparing and submitting individual tax returns.
		\item Specialised in job expense refunds under ITEPA 2003 Sections 336 and 339, ensuring accurate claims for clients.
		\item Balanced multiple priorities, including tax return preparation, client communication, and compliance documentation, demonstrating strong organisational skills.
        \item Regularly resolved complex client cases, showcasing systematic problem-solving and attention to detail.
	\end{rSubsection}

%------------------------------------------------

	\begin{rSubsection}{Migrant Help}{October 2015 - August 2020}{Senior Telephone and Compliance Advisor }{Dover, Kent}
		\item Guided asylum seekers and third parties through NASS support applications, ensuring compliance with government regulations.
		\item Investigated and resolved complex cases, demonstrating strong attention to detail and problem-solving skills.
        \item Conducted precise compliance checks and managed high-volume interactions with professionalism and effective communication.
	\end{rSubsection}

 %------------------------------------------------

	\begin{rSubsection}{Children with Cancer UK}{September 2014 - October 2015}{Supporter Care Administrator}{Holborn, London}
		\item Served as the first point of contact for inquiries, ensuring efficient and professional communication across multiple channels.
		\item Supported fundraising departments and provided administrative assistance as PA to the CEO.
        \item Coordinated external events, including the London Marathon, demonstrating organisational and teamwork skills.
	\end{rSubsection}
 
\end{rSection}

%----------------------------------------------------------------------------------------
%	EDUCATION SECTION
%----------------------------------------------------------------------------------------

\begin{rSection}{Education}

\begin{rSubsection}{University of Kent}{2023 - 2024}{Computer Science (Artificial Intelligence) MSc}{Canterbury, Kent}
    \item Achieved distinctions in all completed modules; final marks pending dissertation assessment. 
    \item The course provided a comprehensive foundation in machine learning, data mining, and software development, with practical coding experience gained through hands-on projects.
    \item Dissertation: "\textit{Modelling Quantum-Classical Interactions: A Comparative Study of Q-UML and Quantum UML Profile Diagrams for the Variational Quantum Eigensolver in Qiskit}."
\end{rSubsection}

\begin{rSubsection}{London South Bank University}{2011 - 2014}{Creative Writing BA Hons}{South Bank, London}
    \item Developed a portfolio of written work, including screenplays, essays, and structured narratives.
\end{rSubsection}

\begin{rSubsection}{Canterbury College}{2007 - 2011}{A-Level \& AS Level}{Canterbury, Kent}
    \item Three A-levels and one AS level in Film Studies, Media Studies, English Literature \& Language, and Anthropology.
\end{rSubsection}

\begin{rSubsection}{Folkestone School for Girls}{2003 - 2007}{GCSE}{Folkestone, Kent}
    \item Nine GCSEs in Additional Science, Maths, English \& English Literature, Geography, History, Religious Studies, Citizenship, and Drama.
\end{rSubsection}

\end{rSection}

%	Extracurricular
%----------------------------------------------------------------------------------------

\begin{rSection}{Extracurricular}

I enjoy creative writing and participating in challenges like National Novel Writing Month. One of my projects includes a "choose your own adventure" book inspired by Dungeons and Dragons. I stay active by regularly going to the gym and exploring new activities. I love charity shopping and am passionate about collecting soft toys and memorabilia. 

\end{rSection}
%----------------------------------------------------------------------------------------

%----------------------------------------------------------------------------------------



%	EXAMPLE SECTION
%----------------------------------------------------------------------------------------

%\begin{rSection}{Section Name}

	%Section content\ldots

%\end{rSection}

%----------------------------------------------------------------------------------------

\end{document}
